MS Depression Paper, post replication, started 2022 09 21

### 2022-10-06 msdepression/scripts/MS_Depression_First_Paper_started_20220728/msdepression_n380_started_2022092022_post_replication.Rmd
Add files via upload

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(visreg)
library(lme4)
library(lmerTest)
library(ggplot2)
library(reshape2)
library(pwr)
library(mgcv)
library(boot)
library(boot.pval)
library(lsr)
library(sjPlot)
library(coin)
library(rstatix)
library(effectsize)
library(colormod)
library(ggpubr)

@@

#goal is to keep people who were seen by 
 data_empi_acc_f_phq <- data %>% 
   mutate(across(.cols = columns_to_make_integer, .fns = as.integer)) %>%
   mutate(sex_binarized = ifelse(SEX == "MALE", 1, 2)) %>%
   mutate(osex = ordered(sex_binarized,levels = c(1,2), labels = c("Male","Female"))) %>%
   mutate(race_binarized = ifelse(RACE == "WHITE", 1, 2)) %>%
   mutate(orace = ordered(race_binarized,levels = c(1,2), labels = c("White","Non-white"))) %>%
   mutate(EXAM_DATE = as.Date(BEGIN_EXAM_DTTM, format = "%m/%d/%y")) %>% 
   mutate(EXAM_DATE = gsub(EXAM_DATE, pattern = "-", replacement = "")) %>%
   mutate(BEGIN_EXAM_DTTM = as.Date(BEGIN_EXAM_DTTM, format = "%m/%d/%y")) %>% #make sure to actually save it as date object for later processing
   mutate(EMPI = as.factor(EMPI)) %>%
   mutate(On.Psych.Meds = ifelse(On.Psych.Meds == "True", 1, 0)) %>%
   mutate(On.Antidepressants = ifelse(On.Antidepressants == "True", 1, 0)) %>%
   mutate(Has.PHQ2 = ifelse(Has.PHQ2 == "True", 1, 0)) %>%
   mutate(Has.PHQ9 = ifelse(Has.PHQ9 == "True", 1, 0)) %>%
   mutate(Has.depdx = ifelse(grepl("F3", ICD10), 1, 0)) %>%
   mutate(PHQ.2_modsev_dep_sxs = ifelse((!is.na(PHQ.2) & PHQ.2 >= 3), 1, 0)) %>%
   mutate(PHQ.9_modsev_dep_sxs = ifelse((!is.na(PHQ.9) & PHQ.9 >= 10), 1, 0)) %>%
   mutate(PHQ.2_mild_dep_sxs = ifelse((!is.na(PHQ.2) & PHQ.2 > 0 & PHQ.2 < 3), 1, 0)) %>%
   mutate(PHQ.9_mild_dep_sxs = ifelse((!is.na(PHQ.9) & PHQ.9 > 0 & PHQ.9 < 10), 1, 0)) %>%
   mutate(PHQ.2_zero = ifelse((!is.na(PHQ.2) & PHQ.2 == 0), 1, 0)) %>%
   mutate(PHQ.9_zero = ifelse((!is.na(PHQ.9) & PHQ.9 == 0), 1, 0)) %>%
   mutate(dep_by_dx_phq = ifelse((Has.depdx | PHQ.2_modsev_dep_sxs | PHQ.9_modsev_dep_sxs),1,0)) %>%
   mutate(dep_by_dx_phq_antidep = ifelse((Has.depdx | On.Antidepressants | PHQ.2_modsev_dep_sxs | PHQ.9_modsev_dep_sxs),1,0)) %>%
   mutate(true_healthy = ifelse((!Has.depdx & !On.Psych.Meds & (PHQ.2_zero | PHQ.9_zero)), 1, 0)) %>%
   mutate(dep_by_dx_phq_meds_healthy_phq0_no_psych_meds = ifelse(dep_by_dx_phq_antidep | true_healthy, 1, 0)) %>%
   rowwise(ACCESSION_NUM) %>%
   mutate(depGroupVar =
            sum(c(dep_by_dx_phq_meds_healthy_phq0_no_psych_meds,dep_by_dx_phq_antidep))) %>%#you get an extra point if you are in the depression group, so the end result is dep = 2, healthy = 1, 0 for exclude
   ungroup()

@@

fascicle_proportions <- read.csv(paste0(homedir, "/results/fascicle_volumes_all_subjects_roi_n2336.csv"), header = T, sep = ",") #n = 2336

@@

lesion_volumes <- read.csv(paste0(homedir, "/results/mimosa_binary_masks_hcp_space_20211026_n2336_volumes"), sep = ",", header = TRUE)

##########################################################
#             Merge with data_empi              #
##########################################################
#merge whole data set with fascicle proportions
df_demo_and_fascicles <- merge(data_empi_acc_f_phq, fascicle_proportions, by = c("EMPI", "EXAM_DATE")) #n = 2962

@@

```
### PROMIS DATA HANDLING to link a person to their most proximal PROMIS

@@

df_good_mimosa_unique_dep_and_healthy <- df_demo_and_fascicles %>% 
  filter(depGroupVar != 0) %>%
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup() 
make_demographics_table_ms(data_frame = df_good_mimosa_unique_dep_and_healthy)

@@

bar_dep_vs_nondep_scaled_by_network_size <- ggplot(df_proportion_network_volume_and_diagnosis_summary, aes(x=depGroupVar, y=mean, fill=depGroupVar)) +
  geom_bar(stat = "identity", fill=Diagnosis_colors_faded, color = Diagnosis_colors, size = 1.5, width = 0.8) +  
  geom_errorbar(aes(ymin=mean-se,ymax=mean+se), width=0.2, size=1.5, color = 'black') + #, position=position_dodge(width=0.5), width = 0.2,size = 1.5, color='black') +
  scale_x_discrete(labels=c("Non-depressed" = "Nondepressed", "Depressed" = "Depressed")) + 
  ggtitle(paste0("Proportion Fascicle Volume Affected by Diagnosis")) +
  ylab("Proportion (sum total volume lost/Net Vol) ") +
  ylim(0,0.5) + 
  theme(plot.title = element_text(size=16, hjust = 0.55),
        axis.text = element_text(size = 16, colour = "black"), axis.title.x = element_blank(), 
        axis.title.y = element_text(size=16),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        legend.position = "none",
        aspect.ratio=7/5,
        panel.background = element_rect(colour = "white", fill = "white"))
print(bar_dep_vs_nondep_scaled_by_network_size) #

@@

interaction_line <- ggplot(data = df_interaction_fit_upper_lower, aes(x = Network, y = model_data$predicted, color = Diagnosis)) +
  geom_line(aes(group = Diagnosis), size = 1.5) +
  scale_color_manual(values=Diagnosis_colors, labels=Diagnosis_labels)+ 
  geom_point(size = 3) + 
 # geom_errorbar(aes(ymin=model_data$conf.low,ymax=model_data$conf.high), width = 0.2,size = 1, color='black') +
  scale_x_discrete(labels=Network_labels) +
  ylim(0,0.5) + 
    xlab("Diagnosis") + 
    ylab("Proportion Affected") + 
    theme(axis.text.x = element_text(size=16, color="black"),
          axis.text.y = element_text(size=16, color="black"),
          axis.title.x = element_blank(), #element_text(size =16), 
          axis.title.y = element_text(size =16), 
          title = element_text(size=18),
          axis.line = element_line(size = 1.5, colour = "black", linetype=1),
          aspect.ratio = 7/5,
          panel.background = element_rect(colour = "white", fill = "white"),
          legend.key=element_blank(),
          legend.title = element_blank(),
          legend.text = element_text(size = 14), legend.position = "top")

#save as pdf
pdf(file=paste0(homedir, "/results/Figures_for_msdepression_paper/diagnosis_by_network_interaction_line_graph_range0to05_point.pdf"))
  interaction_line
dev.off()

@@

#geom_point 0.2-0.5
interaction_ggplot_point_02_05 <- ggplot(data = df_interaction_fit_upper_lower, mapping = aes(x = Diagnosis, y = model_data$predicted, color = Network, group = interaction(Diagnosis, Network))) + 
    geom_errorbar(aes(ymin=model_data$conf.low,ymax=model_data$conf.high), position=position_dodge(width=0.5), width = 0.2,size = 1.5, color='black') +
    geom_point(position = position_dodge(width=0.5), size = 5) + 
    scale_color_manual(values=Network_colors, labels = c("Depression Network", "Nondepression Network")) + 
    ylim(0.2,0.5) + 
    xlab("Diagnosis") + 
    ylab("Proportion Affected") + 
    theme(axis.text.x = element_text(size=16, color="black"),
          axis.text.y = element_text(size=16, color="black"),
          axis.title.x = element_blank(), #element_text(size =16), 
          axis.title.y = element_text(size =16), 
          title = element_text(size=18),
          axis.line = element_line(size = 1.5, colour = "black", linetype=1),
          aspect.ratio = 5/3,
          panel.background = element_rect(colour = "white", fill = "white"),
          legend.key=element_blank(),
          legend.title = element_blank(),
          legend.text = element_text(size = 14), #,
          legend.position = "top") #+ 
 #   ggtitle("Diagnosis x Depression Network Disease")
print(interaction_ggplot_point_02_05)

#save as pdf
pdf(file=paste0(homedir, "/results/Figures_for_msdepression_paper/diagnosis_by_network_interaction_plot_range0_2to0_5_point.pdf"))
  interaction_ggplot_point_02_05
dev.off()

#geom_bar
interaction_ggplot_bar <- ggplot(data = df_interaction_fit_upper_lower, mapping = aes(x = Diagnosis, y = model_data$predicted, color = Network,  group = interaction(Diagnosis, Network))) + 
    geom_col(position = position_dodge(width=0.6), fill = c(Network_colors_faded, Network_colors_faded), color = c(Network_colors, Network_colors), width = 0.5, size = 1.5) + 
    geom_errorbar(aes(ymin=model_data$conf.low,ymax=model_data$conf.high), position=position_dodge(width=0.6), width = 0.2,size = 1.5, color='black') +
    #geom_point(position = position_dodge(width=0.5), size = 5) + 
    scale_color_manual(values=Network_colors) + #, labels = c("Depression Network", "Nondepression Network"))+ 
    ylim(0,0.5) + 
    xlab("Diagnosis") + 
    ylab("Proportion Affected") + 
    theme(axis.text.x = element_text(size=16, color="black"),
          axis.text.y = element_text(size=16, color="black"),
          axis.title.x = element_blank(), #element_text(size =16), 
          axis.title.y = element_text(size =16), 
          plot.title = element_text(size=16, hjust = 0.5),
          axis.line = element_line(size = 1.5, colour = "black", linetype=1),
          aspect.ratio = 7/5,
          panel.background = element_rect(colour = "white", fill = "white"),
          legend.key=element_blank(),
          legend.title = element_blank(),
          legend.text = element_text(size = 14),
          legend.position = "top")+

    ggtitle("Diagnosis x Depression Network Disease")
print(interaction_ggplot_bar)

#save as pdf
pdf(file=paste0(homedir, "/results/Figures_for_msdepression_paper/diagnosis_by_network_interaction_plot_range0to05_bar.pdf"))
  interaction_ggplot_bar
dev.off()

@@

pdf(file=paste0(homedir, "/results/Figures_for_msdepression_paper/diagnosis_intx_line_and_intx_bargraph_range0to05.pdf"))
  diagnosis_and_interaction_bar_combined

@@

pdf(file=paste0(homedir, "/results/Figures_for_msdepression_paper/diagnosis_intx_line_and_intx_bargraph_range0to05.pdf"))
  diagnosis_and_interaction_all_combined
dev.off()
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(visreg)
library(lme4)
library(lmerTest)
library(ggplot2)
library(reshape2)
library(pwr)
library(mgcv)
library(boot)
library(boot.pval)
library(lsr)
library(sjPlot)
library(coin)
library(rstatix)
library(effectsize)
library(colormod)
library(ggpubr)
library(ggsignif)

@@

 data_empi_acc_f_phq <- data %>% 
   mutate(across(.cols = columns_to_make_integer, .fns = as.integer)) %>%
   mutate(sex_binarized = ifelse(SEX == "MALE", 1, 2)) %>%
   mutate(osex = ordered(sex_binarized,levels = c(1,2), labels = c("Male","Female"))) %>%
   mutate(race_binarized = ifelse(RACE == "WHITE", 1, 2)) %>%
   mutate(orace = ordered(race_binarized,levels = c(1,2), labels = c("White","Non-white"))) %>%
   mutate(EXAM_DATE = as.Date(BEGIN_EXAM_DTTM, format = "%m/%d/%y")) %>% 
   mutate(EXAM_DATE = gsub(EXAM_DATE, pattern = "-", replacement = "")) %>%
   mutate(BEGIN_EXAM_DTTM = as.Date(BEGIN_EXAM_DTTM, format = "%m/%d/%y")) %>% #make sure to actually save it as date object for later processing
   mutate(EMPI = as.factor(EMPI)) %>%
   mutate(On.Psych.Meds = ifelse(On.Psych.Meds == "True", 1, 0)) %>%
   mutate(On.Antidepressants = ifelse(On.Antidepressants == "True", 1, 0)) %>%
   mutate(Has.PHQ2 = ifelse(Has.PHQ2 == "True", 1, 0)) %>%
   mutate(Has.PHQ9 = ifelse(Has.PHQ9 == "True", 1, 0)) %>%
   mutate(Has.depdx = ifelse(grepl("F3", ICD10), 1, 0)) %>%
   mutate(PHQ.2_modsev_dep_sxs = ifelse((!is.na(PHQ.2) & PHQ.2 >= 3), 1, 0)) %>%
   mutate(PHQ.9_modsev_dep_sxs = ifelse((!is.na(PHQ.9) & PHQ.9 >= 10), 1, 0)) %>%
   mutate(PHQ.2_mild_dep_sxs = ifelse((!is.na(PHQ.2) & PHQ.2 > 0 & PHQ.2 < 3), 1, 0)) %>%
   mutate(PHQ.9_mild_dep_sxs = ifelse((!is.na(PHQ.9) & PHQ.9 > 0 & PHQ.9 < 10), 1, 0)) %>%
   mutate(PHQ.2_zero = ifelse((!is.na(PHQ.2) & PHQ.2 == 0), 1, 0)) %>%
   mutate(PHQ.9_zero = ifelse((!is.na(PHQ.9) & PHQ.9 == 0), 1, 0)) %>%
   mutate(dep_by_dx_phq = ifelse((Has.depdx | PHQ.2_modsev_dep_sxs | PHQ.9_modsev_dep_sxs),1,0)) %>%
   mutate(dep_by_dx_phq_antidep = ifelse((Has.depdx | On.Antidepressants | PHQ.2_modsev_dep_sxs | PHQ.9_modsev_dep_sxs),1,0)) %>%
   mutate(true_healthy = ifelse((!Has.depdx & !On.Psych.Meds & (PHQ.2_zero | PHQ.9_zero)), 1, 0)) %>%
   mutate(dep_by_dx_phq_meds_healthy_phq0_no_psych_meds = ifelse(dep_by_dx_phq_antidep | true_healthy, 1, 0)) %>%
   rowwise(ACCESSION_NUM) %>%
   mutate(depGroupVar =
            sum(c(dep_by_dx_phq_meds_healthy_phq0_no_psych_meds,dep_by_dx_phq_antidep))) %>%#you get an extra point if you are in the depression group, so the end result is dep = 2, healthy = 1, 0 for exclude
   ungroup() #n=3,737 unique people, n= 16,830 total

@@

fascicle_proportions <- read.csv(paste0(homedir, "/results/fascicle_volumes_all_subjects_roi_n2336.csv"), header = T, sep = ",") #n = 2336, n unique = 958

#change empi to factor

fascicle_proportions$EMPI = as.factor(fascicle_proportions$EMPI)

@@

lesion_volumes <- read.csv(paste0(homedir, "/results/mimosa_binary_masks_hcp_space_20211026_n2336_volumes"), sep = ",", header = TRUE) #n=958 unique, identical to fascicle unique

lesion_volumes$EMPI <- as.factor(lesion_volumes$EMPI)

##########################################################
#             Merge with data_empi              #
##########################################################
#merge whole data set with fascicle proportions
df_demo_and_fascicles <- merge(data_empi_acc_f_phq, fascicle_proportions, by = c("EMPI", "EXAM_DATE")) #n = 2962, unique = 783

@@

```{r get_mimosa_QC_info}

#This section checks how many unique individuals had QA data, and then how many met MIMoSA QC. Some additional people lost at registration.

#1 Total unique individuals who also have MS - 890
#2 Total unique who had good MIMoSA - 786
#3 Total unique with bad MIMoSA - 890-786 = 104
#4 Total lost in streamline filtering - 3
#5 Final N going into inclusion/exclusion - 783

#read in mimosa data
mimosa_qc <- read.csv(paste0(homedir, "/data/melissa_martin_files/csv/mimosa_dataframe"), sep = ",", header = FALSE) #n=2840

#preprocess data frame to extract dates, empis, and score
empis_with_qc <- mimosa_qc %>% 
  mutate(EMPI = as.factor(gsub(x = V5, pattern = ".*sub-(.*)/ses-.*/.*", replacement="\\1", perl = TRUE))) %>%
  mutate(EXAM_DATE = gsub(x=V5, pattern = ".*/ses-(.{8})/.*", replacement = "\\1\\2\\3")) %>% 
  mutate(score = V3)

#merge with whole data frame to make sure we exclude people w/out MS
mimosa_qc_with_data_empi_acc_f_phq <- merge(data_empi_acc_f_phq, empis_with_qc, by = c("EMPI", "EXAM_DATE")) #n = 3592

#get list of unique patients, n = 890
mimosa_qc_with_data_empi_acc_f_phq_unique <- mimosa_qc_with_data_empi_acc_f_phq %>%
  group_by(EMPI) %>%
  arrange(EXAM_DATE) %>%
  slice(1) %>%
  ungroup #n=890

#get list of unique patients with good QC, n = 786
mimosa_unique_score_gre_75 <- mimosa_qc_with_data_empi_acc_f_phq %>%
  filter(score >= 75) %>%
  group_by(EMPI) %>%
  arrange(EXAM_DATE) %>%
  slice(1) %>%
  ungroup #n=786

#merge with fascicle proportions, we lose 3
mimosa_qc_with_data_empi_acc_f_phq_fascicle_props <- merge(mimosa_qc_with_data_empi_acc_f_phq, fascicle_proportions, by = c("EMPI", "EXAM_DATE")) #n=2962

mimosa_qc_with_data_empi_acc_f_phq_fascicle_props_unique <- mimosa_qc_with_data_empi_acc_f_phq_fascicle_props %>% 
  group_by(EMPI) %>%
  arrange(EXAM_DATE) %>%
  slice(1) %>%
  ungroup #n=783
```

### PROMIS DATA HANDLING to link a person to their most proximal PROMIS

@@

df_good_mimosa_unique_dep_and_healthy <- df_demo_and_fascicles_prop_and_vol %>% 
  filter(depGroupVar != 0) %>%
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup() 
make_demographics_table_ms(data_frame = df_good_mimosa_unique_dep_and_healthy)

@@

bar_dep_vs_nondep_scaled_by_network_size <- ggplot(df_proportion_network_volume_and_diagnosis_summary, aes(x=depGroupVar, y=mean, fill=depGroupVar)) +
  geom_bar(stat = "identity", fill=Diagnosis_colors_faded, color = Diagnosis_colors, size = 1.5, width = 0.8) +  
  geom_errorbar(aes(ymin=mean-se,ymax=mean+se), width=0.2, size=1.5, color = 'black') + #, position=position_dodge(width=0.5), width = 0.2,size = 1.5, color='black') +
  scale_x_discrete(labels=c("Non-depressed" = "Nondepressed", "Depressed" = "Depressed")) + 
#  ggtitle(paste0("Proportion Fascicle Volume Affected by Diagnosis")) +
  ylab("Proportion of Whole Brain White Matter Volume Affected") +
  ylim(0,0.6) + 
  theme(plot.title = element_text(size=14, hjust = 0.55),
        axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
        axis.title.y = element_text(size=14),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        legend.position = "none",
        aspect.ratio=7/5,
        panel.background = element_rect(colour = "white", fill = "white"))
print(bar_dep_vs_nondep_scaled_by_network_size) #

@@

interaction_line <- ggplot(data = df_interaction_fit_upper_lower, aes(x = Network, y = model_data$predicted, color = Diagnosis)) +
  geom_line(aes(group = Diagnosis), size = 1.5) +
  scale_color_manual(values=Diagnosis_colors, labels=Diagnosis_labels)+ 
  geom_point(size = 3) + 
 # geom_errorbar(aes(ymin=model_data$conf.low,ymax=model_data$conf.high), width = 0.2,size = 1, color='black') +
  scale_x_discrete(labels=Network_labels) +
  ylim(0,0.6) + 
    xlab("Diagnosis") + 
    ylab("Proportion Affected") + 
    theme(axis.text.x = element_text(size=16, color="black"),
          axis.text.y = element_text(size=16, color="black"),
          axis.title.x = element_blank(), #element_text(size =16), 
          axis.title.y = element_text(size =16), 
          title = element_text(size=18),
          axis.line = element_line(size = 1.5, colour = "black", linetype=1),
          aspect.ratio = 7/5,
          panel.background = element_rect(colour = "white", fill = "white"),
          legend.key=element_blank(),
          legend.title = element_blank(),
          legend.text = element_text(size = 14), legend.position = "top")

#save as pdf
pdf(file=paste0(homedir, "/results/Figures_for_msdepression_paper/diagnosis_by_network_interaction_line_graph_range0to06_point.pdf"))
  interaction_line
dev.off()

@@

#geom_point 0.2-0.5
interaction_ggplot_point_02_06 <- ggplot(data = df_interaction_fit_upper_lower, mapping = aes(x = Diagnosis, y = model_data$predicted, color = Network, group = interaction(Diagnosis, Network))) + 
    geom_errorbar(aes(ymin=model_data$conf.low,ymax=model_data$conf.high), position=position_dodge(width=0.5), width = 0.2,size = 1.5, color='black') +
    geom_point(position = position_dodge(width=0.5), size = 5) + 
    scale_color_manual(values=Network_colors, labels = c("Depression Network", "Nondepression Network")) + 
    ylim(0.2,0.6) + 
    xlab("Diagnosis") + 
    ylab("Proportion Affected") + 
    theme(axis.text.x = element_text(size=16, color="black"),
          axis.text.y = element_text(size=16, color="black"),
          axis.title.x = element_blank(), #element_text(size =16), 
          axis.title.y = element_text(size =16), 
          title = element_text(size=18),
          axis.line = element_line(size = 1.5, colour = "black", linetype=1),
          aspect.ratio = 5/3,
          panel.background = element_rect(colour = "white", fill = "white"),
          legend.key=element_blank(),
          legend.title = element_blank(),
          legend.text = element_text(size = 14), #,
          legend.position = "top") #+ 
 #   ggtitle("Diagnosis x Depression Network Disease")
print(interaction_ggplot_point_02_06)

#save as pdf
pdf(file=paste0(homedir, "/results/Figures_for_msdepression_paper/diagnosis_by_network_interaction_plot_range0_2to0_6_point.pdf"))
  interaction_ggplot_point_02_06
dev.off()

#geom_bar
interaction_ggplot_bar <- ggplot(data = df_interaction_fit_upper_lower, mapping = aes(x = Diagnosis, y = model_data$predicted, color = Network,  group = interaction(Diagnosis, Network))) + 
    geom_col(position = position_dodge(width=0.6), fill = c(Network_colors_faded, Network_colors_faded), color = c(Network_colors, Network_colors), width = 0.5, size = 1.5) + 
    geom_errorbar(aes(ymin=model_data$conf.low,ymax=model_data$conf.high), position=position_dodge(width=0.6), width = 0.2,size = 1.5, color='black') +
    scale_fill_manual(values=Network_colors) + #, labels = c("Depression Network", "Nondepression Network"))+ 
    ylim(0,0.6) + 
    xlab("Diagnosis") + 
    ylab("Proportion of White Matter Network Affected") + 
    theme(axis.text.x = element_text(size=14, color="black"),
          axis.text.y = element_text(size=14, color="black"),
          axis.title.x = element_blank(), #element_text(size =16), 
          axis.title.y = element_text(size =14), 
          plot.title = element_text(size=16, hjust = 0.5),
          axis.line = element_line(size = 1.5, colour = "black", linetype=1),
          aspect.ratio = 7/5,
          panel.background = element_rect(colour = "white", fill = "white"))+

    geom_signif(
      y_position = c(0.48, 0.48, 0.53, 0.58), 
      xmin = c(0.85, 1.85, 0.85, 1.15),
      xmax = c(1.15, 2.15, 1.85, 2.15),
      annotation = c("***", "***", "*", "NS"), 
      tip_length = 0.03, color = "black",
      size = 1.1, textsize = 5) #+
  #  ggtitle("Diagnosis x Depression Network Disease")
print(interaction_ggplot_bar)

#save as pdf
pdf(file=paste0(homedir, "/results/Figures_for_msdepression_paper/diagnosis_by_network_interaction_plot_range0to06_bar.pdf"))
  interaction_ggplot_bar
dev.off()

@@

print(diagnosis_and_interaction_bar_combined)
pdf(file=paste0(homedir, "/results/Figures_for_msdepression_paper/diagnosis_and_intx_bargraph_range0to06.pdf"))
  diagnosis_and_interaction_bar_combined

@@

pdf(file=paste0(homedir, "/results/Figures_for_msdepression_paper/diagnosis_intx_line_and_intx_bargraph_range0to06.pdf"))
  diagnosis_and_interaction_all_combined
dev.off()
```
